New MSK samples

### 2020-12-07 scripts/39_new_MSK_shotgun.Rmd
update

pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') # the 33 used last year
intersect(pheno$sampleid, ineligible$sampleid)  # 6 has become ineligible 
```

@@

pheno_msk <- current_Baseline %>% 
  select(mrn:sampleid, fid) %>% 
  left_join(ptb)

pheno_msk %>% 
  write_csv('../data/shotgun_pheno/msk_all_pheno.csv')
```

>>>>

pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') # the 33 used last year
intersect(pheno$sampleid, ineligible$sampleid)  # 6 has become ineligible

setdiff(current_Baseline$sampleid, pheno$sampleid)

missing <- c("2460A", "2563A", "1918C" ,"315"  )
```

@@

pheno_msk <- current_Baseline %>% 
  select(mrn:sampleid, fid, directory) %>% 
  left_join(ptb)

pheno_msk %>% 
  write_csv('../data/shotgun_pheno/msk_all_pheno.csv')

pheno_msk %>% 
  filter(sampleid %in% missing)
```
